Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-20 documents/mixtures/mixture_models.tex
acks

The results of the optimizations are shown in \tablename
s~\ref{tab:exp} through \ref{tab:luv} and \figurename s~\ref{fig:exp}
through \ref{fig:M}... Discuss briefly the import of it all... Why in
the tables are we giving and plotting root-variances not variances?...

@@

\acknowledgements It is a pleasure to thank
      Brendon Brewer (Auckland)
  and Kevin Bundy (IPMU)
for valuable comments.  This work was supported in part by NASA (grant
NNX12AI50G) and the NSF (grant IIS-1124794).

>>>>

The results of the optimizations are shown in \tablename
s~\ref{tab:exp} through \ref{tab:luv} and \figurename s~\ref{fig:exp}
through \ref{fig:M}.  All the results shown in these figures and
tables and more are available in machine-readable form from author DWH
upon request.  In the \tablename s and \figurename s we show
root-variances rather than variances because these have units of
half-light radii; they are simple standard deviations for the Gaussian
components.

@@

\acknowledgements It is a pleasure to thank
      Brendon Brewer (Auckland)
  and Kevin Bundy (IPMU)
for valuable comments.  This work was supported in part by NASA (grant
NNX12AI50G) and the NSF (grant IIS-1124794).  All the results shown in
the figures and tables and more are available in machine-readable form
from author DWH upon request.
